\Huge Conferences in the Era of Expensive Carbon

### 2019-10-15 main.tex
CP

\bcp{Richard Kim sent a bunch of great comments!  In particular...
  \begin{itemize}
  \item (a) You might say something more about how ACM is in a good position
  to set a trend -- something about taking leadership among scientific
  societies or being on the forefront. There's a little bit about this at
  the end, but it might be developed more into a sentence or paragraph. You
  probably want to phrase this as leadership as opposed to say, sticking
  one's neck out, but there could be something about how computer science and
 tech folks are current and forward-looking, and it's consistent that we
 not be behind the leading edge.
 \item (b) You might say more how ACM needs to prepare itself in light of
 the trends that are coming -- carbon pricing is good organizational sense!
 There's some of this around ACM's potentially needing to adjust its
 business model, but it falls short of making a *business case for carbon
 pricing*, which is what I guess I'm recommending.
 \item Also, in addition to mentioning that Microsoft and other tech
 companies set a price on carbon, you might also note here that Exxon and
 other energy companies set an internal price on carbon as well, as a means
 of risk assessment. In other words, even the oil companies know what's
 coming.
 \end{itemize}
}

@@

Indeed, scientific societies arguably have an especially important role to
play, since, for many of their members, travel to conferences may be a
substantial or even dominant part of their individual contribution to
climate change.  A single round-trip flight from Philadelphia to Paris emits
the equivalent of about 1.7 tons of carbon dioxide (\COtwoE) per
passenger\iflater\bcp{Citation?}\fi, which is a significant fraction of the
{\em total} yearly emissions for an average resident of the US (16.5 tons)
or Europe (7 tons)~\cite{emissions}.  
Moreover, these emissions have no near-term technological
fix, since jet fuel is difficult to replace with renewable energy
sources~\cite{elec-air}.
% \iflater\bcp{Trimmed this sentence: Reducing the \COtwoE{} footprint
% of conferences will require a reduction in the footprint of the attendees'
% air travel.}\fi

>>>>

@@

Indeed, scientific societies arguably have an especially important role to
play, since, for many of their members, travel to conferences may be a
substantial or even dominant part of their individual contribution to
climate change.  A single round-trip flight from Philadelphia to Paris emits
the equivalent of about 1.7 tons of carbon dioxide (\COtwoE) per
passenger\iflater\bcp{Citation?}\fi, a significant fraction of the
{\em total} yearly emissions for an average resident of the US (16.5 tons)
or Europe (7 tons)~\cite{emissions}.  
Moreover, these emissions have no near-term technological
fix, since jet fuel is difficult to replace with renewable energy
sources~\cite{elec-air}.
% \iflater\bcp{Trimmed this sentence: Reducing the \COtwoE{} footprint
% of conferences will require a reduction in the footprint of the attendees'
% air travel.}\fi
